Synthesis report

### 2020-05-07 analysis/reports/figs.Rmd
with fia small

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log150_nparts = log(gmp:::as.double.bigz(nparts), base = 150)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1) %>%
  filter(s0 >= 2,
         n0 > s0,
         dat != "fia_small")
```

@@

ggplot(filter(all_di, !singletons, dat != "fia_short"), aes(x = skew_percentile)) +
  geom_histogram() +
  theme_bw()

ggplot(filter(all_di, !singletons, dat != "fia_short"), aes(x = simpson_percentile)) +
  geom_histogram() +
  theme_bw()

>>>>

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log150_nparts = log(gmp:::as.double.bigz(nparts), base = 150)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1) %>%
  filter(s0 >= 2,
         n0 > s0)
```

@@

ggplot(filter(all_di, !singletons, dat != "fia_short", dat != "fia_small"), aes(x = skew_percentile)) +
  geom_histogram() +
  theme_bw()

ggplot(filter(all_di, !singletons, dat != "fia_short", dat != "fia_small"), aes(x = simpson_percentile)) +
  geom_histogram() +
  theme_bw()
